---
title: "| Empirical Strategy: \n| Capital Adequacy Arbitrage and Bank Lending\n"
author: "Lucas Avezum"
date: "May 14, 2019"
output:
  pdf_document: default
  html_document: default
bibliography: bibliography/references.bib
---

```{r install, eval = FALSE, include=FALSE}
## This code will not be evaluated automatically.
## (Notice the eval = FALSE declaration in the options section of the
## code chunk)

my_packages <- c("tidyverse", "broom", "coefplot", "cowplot",
                 "gapminder", "GGally", "ggrepel", "ggridges",
                 "gridExtra","here", "interplot", "margins", "maps",
                 "mapproj","mapdata", "MASS", "quantreg", "rlang",
                 "scales","survey", "srvyr", "viridis", "viridisLite",
                 "devtools","xlsx","plm","stringr","lfe","robustHD","DescTools","stargazer")

install.packages(my_packages, repos = "http://cran.rstudio.com")
```


```{r setup, eval = FALSE, include=FALSE}
## Project set up 

## By defult, show code for all chunks in the knitted document,
## as well as the output. To override for a particular chunk
## use echo = FALSE in its options.
knitr::opts_chunk$set(echo = TRUE) 

## Set the default size of figures
knitr::opts_chunk$set(fig.width=8, fig.height=5)  

## Load the libraries we will be using
library(here)
library(socviz)
library(tidyverse)
library(reshape2)
library(stringr)
library(xlsx)
library(plm)
library(lfe)
library(DescTools)
library(stargazer)

```




# Empirical model

$log(volume_{b,f,c,t})=\beta\widehat{RW}_{b,t}+\alpha_{b,t}+\alpha_{f,t}+\varepsilon_{b,f,c,t}$ \newline

$log(volume_{b,f,c,t})$ is the log volume of the amount lend by bank $b$ hosted in country $c$ to firm $f$ at time $t$. We can also see $f$ as indexing loans facility. $\alpha_{b,t}$ and $\alpha_{f,t}$ are time-varying bank and loan fixed effects. The variable of interest, $\widehat{RW}_{b,t}$, captures exogenous changes in risk-weight and it is obtained as the fitted value for the following first stage regression: \newline

$RW_{b,t}=\gamma_0 IRB_{b,t}+\gamma_1 IRB_{c,t}+\gamma_2 \overline{RW}_{-b,c,t}+\alpha_{b}+\alpha_{t}+\varepsilon_{b,t}$ \newline


$RW_{b,t}$ is the risk-weight of exposures of bank $b$ at time $t$. For the years before IRB approval $RW_{b,t}$ takes the SA risk-weight. After approval this variable takes the IRB risk-weight. The first instrument, $IRB_{b,t}$, is a dummy variable that takes 1 for the periods after bank $b$ is allowed to calculate risk-weights using IRB models. The second instrument, $IRB_{c,t}$, is a dummy variable that takes 1 when country $c$ implemented Basel II. The third instrument, $\overline{RW}_{-b,c,t}$ is the average risk-weight across all banks headquarted in country $c$, excluding bank $b$. $\alpha_{b}$ and $\alpha_{t}$ are bank and time fixed effects.\newline

**Hypothesis** *$\beta<0$: risk-weight arbitrage leads to competitive advantages.*

# Empirical strategy

$IRB_{b,t}$ and $IRB_{c,t}$ instrument for the time variation in risk-weights as the approval date is exogenous to the bank. This instrument allow us to estimate the exogenous impact of changes in risk-weight on lending. However, it does not inform us about differences in supervisory standard. For this purpose, we include $\overline{RW}_{c,t}$. This measure tries to capture the exogenous cross-section of the supervisory leniency/standard. Note, $\overline{RW}_{c,t}$ fails as a proxy for supervisory stardard in the case that banks within the same jurisdiction systematically have the same risk preference.\newline


Following our discussion, we could also try alternative measures. After approval, $RW_{b,t}$ can be calculated as the weighted average by exposure between SA and IRB risk-weights, as the effect should be stronger for banks with a larger share of their corporate portfolio under IRB (larger probability of loan being allocated in the IRB portfolio). Instead of a binary variable $IRB_{b,t}$ could take the initial share of the corporate portfolio that was approved to be calculated using IRB. This alteration would give us some cross-section variation, but it only make sense if we expect that the amount approved was constrained by the supervisory authority and not a bank's choice. Lastly, we can limit our analysis to loans where we have external rating information, we can estimate the effect of differences in risk-weight within a specific credit risk cluster (AAA, BB+, etc...). This modification helps us to rule out the possibility that the effect that we estimate is not driven by differences in portfolio risk (intended effect).\newline   


# Data

Loan information comes from the Loan Connector, banks' balance sheet information from Orbis/Bankscope. We are collecting from pillar-III reports the date of IRB approval for each bank (we already have for most European banks), risk-weight and exposure amount for IRB and SA portfolios (for corporate and total). For IRB we are also collecting for each bank the risk-weight distribution across credit rating/probability of default. 


