---
title: "| Research proposal: \n| Capital Adequacy Arbitrage and Bank Lending\n"
author: "Lucas Avezum"
date: "06/26/2018"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: bibliography/references.bib
---

```{r install, eval = FALSE, include=FALSE}

## This code will not be evaluated automatically.
## (Notice the eval = FALSE declaration in the options section of the
## code chunk)

my_packages <- c("tidyverse", "broom", "coefplot", "cowplot",
                 "gapminder", "GGally", "ggrepel", "ggridges",
                 "gridExtra","here", "interplot", "margins", "maps",
                 "mapproj","mapdata", "MASS", "quantreg", "rlang",
                 "scales","survey", "srvyr", "viridis", "viridisLite",
                 "devtools","xlsx","readxl","XLConnect","data.table","plm","stringr","lfe","robustHD","DescTools","stargazer")

install.packages(my_packages, repos = "http://cran.rstudio.com")

```



```{r setup, include=FALSE}
## Project set up 

## Clean list
rm(list = ls())

options(java.parameters = "-Xmx4g" ) 


## By defult, show code for all chunks in the knitted document,
## as well as the output. To override for a particular chunk
## use echo = FALSE in its options.
knitr::opts_chunk$set(echo = TRUE) 

## Set the default size of figures
knitr::opts_chunk$set(fig.width=8, fig.height=5)  

## Set working directory
knitr::opts_knit$set(root.dir = ".")


## Load the libraries we will be using
library(here)
library(tidyverse)
library(reshape2)
library(stringr)
library(XLConnect)
library(data.table)
library(plm)
library(lfe)
library(DescTools)
library(stargazer)
library(stringdist)

```


```{r load_merge_EBA, include=FALSE}
## Load
credit_2017 <- read.csv("../../../../data/Financial/EBA-transparency_exercise/2017/tr_cre.csv")
credit_2016 <- read.csv("../../../../data/Financial/EBA-transparency_exercise/2016/tr_cre.csv")
credit_2015 <- read.csv("../../../../data/Financial/EBA-transparency_exercise/2015/tr_cre.csv")
## Drop variables not in common
credit_2017[,c("footnote","Label")] <- NULL
credit_2016[,c("footnote","Label")] <- NULL
credit_2015[,c("footnote","Label")] <- NULL
## Rename amount variable
credit_2015 <- plyr::rename(credit_2015,c("AMOUNT"="Amount","LEI_code"="LEI_Code"))
## Append
credit <- rbind(credit_2017,credit_2016,credit_2015)
## Drop original files
rm(credit_2017,credit_2015,credit_2016)

```

```{r id, include=FALSE}
## Load table with change in indentifiers
ID.df <- readWorksheetFromFile("../../../../data/Financial/EBA-transparency_exercise/2017/TR_Metadata.xlsx",1,startRow=2)

## Create unique identifier
ID.df <- tibble::rowid_to_column(ID.df, "ID")

## Drop unused variables
ID.df[,c("Finrep","Fin_year_end","Periods","TR_16","TR_15")] <- NULL

## Turn data frame in long format
ID.df <- melt(ID.df, id.vars = c("ID","Country","Desc_country","SSM","Name"),
            variable.name = "index", 
            value.name = "LEI_Code")

## Remove variable created by long transformation
ID.df[,c("index")] <- NULL

## Remove duplicated observations and with missing values
ID.df <- unique(ID.df)
ID.df <- na.omit(ID.df)

```

```{r load_Dealscan_facility, include=FALSE}
setwd("../../../../data/Financial/Dealscan/Dealscan_Raw/Facility/")
## Load
temp <-  list.files(pattern="*.xls")
list <-  lapply(temp, readWorksheetFromFile,sheet = 1)
facility.df <- rbindlist(list, use.names=TRUE)
rm(list)
```

```{r load_Dealscan_tranche, include=FALSE}
setwd("../../../../data/Financial/Dealscan/Dealscan_Raw/Tranche/")
## Load
temp <-  list.files(pattern="*.xls")
list <-  lapply(temp, readWorksheetFromFile,sheet = 1)
tranche.df <- rbindlist(list, use.names=TRUE)
rm(list)
```

```{r load_Dealscan_deal, include=FALSE}
setwd("../../../../data/Financial/Dealscan/Dealscan_Raw/Deal/")
## Load
temp <-  list.files(pattern="*.xls")
list <-  lapply(temp, readWorksheetFromFile,sheet = 1)
deal.df <- rbindlist(list, use.names=TRUE)
rm(list)
```


```{r EBA_DealScan_identifier, include= FALSE}
# Create data frames for names of each dataset
EBA.name <- data.frame(ID.df$Name)
names(EBA.name)[names(EBA.name)=="ID.df.Name"] = "name.EBA"
EBA.name$name.EBA = as.character(EBA.name$name.EBA)
EBA.name = unique(EBA.name) 

DealScan.lender.name <- data.frame(facility.df$Lender.Name)
names(DealScan.lender.name)[names(DealScan.lender.name)=="facility.df.Lender.Name"] = "name.DealScan"
DealScan.parent.name <- data.frame(facility.df$Lender.Parent.Name)
names(DealScan.parent.name)[names(DealScan.parent.name)=="facility.df.Lender.Parent.Name"] = "name.DealScan"

DealScan.name <- rbind(DealScan.parent.name,DealScan.lender.name)
DealScan.name$name.DealScan = as.character(DealScan.name$name.DealScan)
DealScan.name = unique(DealScan.name) 
rm(DealScan.lender.name,DealScan.parent.name)

```

```{r match_1, include= FALSE}
# Match
EBA.name$name.DealScan <- ""

for(i in 1:dim(EBA.name)[1]) {
 x <- agrep(EBA.name$name.EBA[i], DealScan.name$name.DealScan,
 ignore.case=TRUE, value=TRUE,
 max.distance = 0.05, useBytes = TRUE)
 x <- paste0(x,"")
 EBA.name$name.DealScan[i] <- x
}

```
```{r match_2, include= FALSE}
# Match
DealScan.name$name.EBA <- ""

for(i in 1:dim(DealScan.name)[1]) {
 x <- agrep(DealScan.name$name.DealScan[i], EBA.name$name.EBA,
 ignore.case=TRUE, value=TRUE,
 max.distance = 0.05, useBytes = TRUE)
 x <- paste0(x,"")
 DealScan.name$name.EBA[i] <- x
}

```
```{r match_3, include= FALSE}
# Match
start_time <- Sys.time()
distance.methods<-c('osa')
dist.methods<-list()
for(m in 1:length(distance.methods))
{
  dist.name.matrix<-matrix(NA, ncol = length(DealScan.name$name.DealScan),nrow = length(EBA.name$name.EBA))
  for(i in 1:length(DealScan.name$name.DealScan)) {
    for(j in 1:length(EBA.name$name.EBA)) { 
      dist.name.matrix[j,i]<-stringdist(tolower(DealScan.name[i,]),tolower(EBA.name[j,]),method = distance.methods[m])      
    }  
  }
  dist.methods[[distance.methods[m]]]<-dist.name.matrix
}
 
match.s1.s2.matrix<-NULL
for(m in 1:length(dist.methods))
{
 
  dist.matrix<-as.matrix(dist.methods[[distance.methods[m]]])
  min.name.enh<-apply(dist.matrix, 1, base::min)
  for(i in 1:nrow(dist.matrix))
  {
    s2.i<-match(min.name.enh[i],dist.matrix[i,])
    s1.i<-i
    match.s1.s2.matrix<-rbind(data.frame(s2.i=s2.i,s1.i=s1.i,s2name=DealScan.name[s2.i,], s1name=EBA.name[s1.i,], adist=min.name.enh[i],method=distance.methods[m]),match.s1.s2.matrix)
  }
}
# Let's have a look at the results

matched.names.matrix<-dcast(match.s1.s2.matrix,s2.i+s1.i+s2name+s1name~method, value.var = "adist")
end_time <- Sys.time()

print(end_time - start_time)

```

```{r risk_calculation, include=FALSE}

## Select variables
variables <- c("0522","0532","0512","0542")
credit$Item <- sapply(credit$Item,toString)
credit$Item_global <- sapply(credit$Item,str_sub,start= -4)
credit$Item <- NULL

exposure.df <- subset(credit, select = 1:11, 
                        subset = credit$Item_global %in% variables & 
                          credit$Exposure %in% 303)

## Split Item variables in exposures variables
exposure.df <- dcast(exposure.df, LEI_Code + NSA + Period + Portfolio + Country + Country_rank ~ Item_global, value.var="Amount")

## Rename variables
exposure.df <- plyr::rename(exposure.df,c("0522"="Exposure","0532"="Risk_exposure","0512"="Exposure_default","0542"="Risk_exposure_default"))

## Remove defaulted exposures from IRB exposures 
exposure.df <- mutate(exposure.df,Exposure_adj = ifelse(is.na(Exposure_default),Exposure,Exposure-Exposure_default))

exposure.df <- mutate(exposure.df,Risk_exposure_adj = ifelse(is.na(Risk_exposure_default),Risk_exposure,Risk_exposure-Risk_exposure_default))

## Create Risk weight variable
exposure.df <- mutate(exposure.df,Risk_weight = Risk_exposure_adj/Exposure_adj)

```

```{r merge, include=FALSE}
exposure.id.df <- merge(ID.df,exposure.df,by="LEI_Code")

## Order observations by unique ID
exposure.id.df <- exposure.id.df[order(exposure.id.df$ID,exposure.id.df$Country.y,exposure.id.df$Period),]
```



```{r cleaning, include=FALSE}

## Keep only obs. per exposed country
exposure.id.df <- exposure.id.df[exposure.id.df$Country.y>0,]

## Remove negative risk weights
exposure.id.df <- exposure.id.df[complete.cases(exposure.id.df$Risk_weight),]
exposure.id.df <- exposure.id.df[exposure.id.df$Risk_weight>0,]

## Create risk calculation method factor
exposure.id.df <- mutate(exposure.id.df,Approach = factor(ifelse(Portfolio==1,"SA","IRB")))

## Create factors for fixed effects
exposure.id.df$ID <- factor(exposure.id.df$ID)
exposure.id.df$Country.y <- factor(exposure.id.df$Country.y)
exposure.id.df$Period <- factor(exposure.id.df$Period)

# Create default rate
exposure.id.df$Default_rate <- exposure.id.df$Risk_exposure_default/exposure.id.df$Risk_exposure
exposure.id.df$Default_rate_w <- Winsorize(exposure.id.df$Default_rate,probs=c(0.05,0.95),na.rm = TRUE)
## Delete old data frames
rm(exposure.df,credit,ID.df)

```

```{r changes, include=FALSE}
## Number of changes to IRB

exposure.id.df <- exposure.id.df %>%
  group_by(ID,Country.y) %>%
  mutate(approach_change = mean(Portfolio),
         approach_change_indicator = ifelse(approach_change==1,"Only SA",
                                            ifelse(approach_change==1.5,"Both",
                                                   ifelse(approach_change==2,"Only IRB","Change"))))

```

```{r density_rw_2, include=TRUE, echo=FALSE}

p <- ggplot(data = exposure.id.df,subset ,
            mapping = aes(x = approach_change_indicator))
p + geom_histogram( stat="count") + geom_text(stat = "count",aes(label = ..count.., y = ..count..))
```

```{r density_rw_oter, echo=FALSE}

p <- ggplot(data = exposure.id.df,
            mapping = aes(x = approach_change, fill = Approach, color = Approach)) 
p + geom_density(alpha = 0.3) + ggtitle("Figure 1: Risk weights density")
```

```{r density_rw_other_again, echo=FALSE}

p <- ggplot(data = subset(exposure.id.df,subset = approach_change_indicator == ""),
            mapping = aes(x = Risk_weight, fill = Approach, color = Approach)) 
p + geom_density(alpha = 0.3) + ggtitle("Figure 1: Risk weights density")
```



```{r density_rw, echo=FALSE}

p <- ggplot(data = subset(exposure.id.df,subset = Risk_weight < 2),
            mapping = aes(x = Risk_weight, fill = Approach, color = Approach)) 
p + geom_density(alpha = 0.3) + ggtitle("Figure 1: Risk weights density")
```



```{r box_plot, echo=FALSE}

p <- ggplot(data = subset(exposure.id.df,subset = Risk_weight < 2),
            mapping = aes(x = reorder(NSA, Risk_weight,FUN = median, na.rm=TRUE),
                          y = Risk_weight,fill=Approach))
p + geom_boxplot() +
    labs(x=NULL) +
    coord_flip() +
    ggtitle("Figure 2: Risk weights distribution by country")
```

```{r box_plot, echo=FALSE}

p <- ggplot(data = subset(exposure.id.df,subset = Risk_weight < 2),
            mapping = aes(x = reorder(Period, Risk_weight,FUN = median, na.rm=TRUE),
                          y = Risk_weight,fill=Approach))
p + geom_boxplot() +
    labs(x=NULL) +
    coord_flip() +
    ggtitle("Figure 2: Risk weights distribution by year")
```


```{r density_exp, echo=FALSE, include=FALSE}


p <- ggplot(data = exposure.id.df,
            mapping = aes(x = log(Exposure), fill = Approach, color = Approach))
p + geom_density(alpha = 0.3)

```
```{r density_default, echo=FALSE,include=FALSE}


p <- ggplot(data = exposure.id.df,
            mapping = aes(x = Default_rate, fill = Approach, color = Approach))
p + geom_density(alpha = 0.3)

```





```{r box_plot_1, echo=FALSE, include=FALSE}

p <- ggplot(data = subset(exposure.id.df,subset = Portfolio == 1),
            mapping = aes(x = reorder(NSA, Risk_weight,FUN = median, na.rm=TRUE),
                          y = Risk_weight))
p + geom_boxplot() +
    labs(x=NULL) +
    coord_flip()
```


```{r box_plot_2, echo=FALSE, include=FALSE}

p <- ggplot(data = subset(exposure.id.df,subset = Portfolio == 2),
            mapping = aes(x = reorder(NSA, Risk_weight,FUN = median, na.rm=TRUE),
                          y = Risk_weight))
p + geom_boxplot() +
    labs(x=NULL) +
    coord_flip()
```

```{r box_plot_3, echo=FALSE, include=FALSE}

p <- ggplot(data = exposure.id.df,
            mapping = aes(x = reorder(Country.y, Risk_weight,FUN = median, na.rm=TRUE),
                          y = Risk_weight))
p + geom_boxplot() +
    labs(x=NULL) +
    coord_flip() +
    facet_wrap(~ Approach,ncol = 2 )
```

```{r reg,echo=FALSE, include=FALSE}
test_1 <- lm(Exposure~Risk_weight,data=exposure.id.df[exposure.id.df$Portfolio == 1,])
summary(test_1)

test_2 <- lm(log(Exposure)~Risk_weight+Default_rate,data=exposure.id.df[exposure.id.df$Portfolio == 2,])
summary(test_2)

test_3 <- lm(log(Exposure)~Risk_weight+Default_rate,data=exposure.id.df)
summary(test_3)
```

 
```{r summary_table,eval=TRUE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

stargazer(as.data.frame(exposure.id.df[c("Exposure","Risk_weight","Default_rate")]),
          header = FALSE, type="latex",
          title = "Summary statistics")
``` 



```{r hdfe,echo=FALSE}
reg.hdfe1 <- felm(log(Exposure)~Risk_weight  | ID:Period + Country.y:Period|0|ID,
                 data = exposure.id.df)


reg.hdfe2 <- felm(log(Exposure)~Risk_weight + Approach +Approach:Risk_weight | ID:Period + Country.y:Period | 0 | ID,
                 data = exposure.id.df)


reg.hdfe3 <- felm(log(Exposure)~Risk_weight + Default_rate | ID:Period + Country.y:Period | 0 | ID,
                 data = exposure.id.df)

reg.hdfe4 <- felm(log(Exposure)~Risk_weight + Default_rate +Risk_weight:Default_rate | ID:Period + Country.y:Period | 0 | ID,
                 data = exposure.id.df)


```

```{r reg)table,eval=TRUE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

stargazer(reg.hdfe1,reg.hdfe2,reg.hdfe3,reg.hdfe4,
          header = FALSE, type="latex",
          title = "Regression results")

```

Next, in column 2 we include a dummy variable that equals 1 if the risk weight is calculated under the standard approach. We interact this dummy variable with risk weight to check if the effect of risk weight is different depending on how it is calculated. The result shows that most of the effect found in the first regression is driven by exposures being systematically lower under the standard approach. The effect of risk weight is found to be smaller for the SA (a positive coefficient for the interaction term) although not statistically significant.

We add the default rate of each exposure as an explanatory variable in regression 3. This variable is only available to exposures under the IRB approach therefore the drop in observations. The effect of risk weight on exposure is estimated somewhat lower but still negative and statistically significant. However, the default rate takes a positive sign, contrary to expectations. Column 4 shows results when we interact default rate with risk weight. The coefficient for risk weights slightly changes and now the effect of default rate is estimated to be negative although not significant different from zero. The interaction term is estimated with the opposite sign. According to **Hypothesis 3** we would expect the coefficient of the interaction term between risk weight and default rate to be negative, suggesting an increase in risk-taking from banks headquarted in countries with more flexible supervision. 







# References



