---
title: "Capital Adequacy Arbitrage and Bank Lending"
author: "Lucas Avezum"
date: "October 23, 2018"
header-includes:
   - \usepackage{bbm,dcolumn,transparent}
output: 
  beamer_presentation:
    theme: "Frankfurt"
    colortheme: "seahorse"
  
bibliography: ../bibliography/references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

rm(list = ls())
getwd()
knitr::opts_chunk$set(fig.width=8, fig.height=5)  

## Load the libraries we will be using
library(tidyverse)
library(reshape2)
library(stringr)
library(plm)
library(lfe)
library(DescTools)
library(stargazer)
library(stringdist)
library(grid)
library(scales)
library(data.table)

load("../../Data/Dataset_clean.Rda")
load("../../Data/EBA.Rda")

```

```{r data_graph, echo=FALSE}
## Remove defaulted exposures from IRB exposures
EBA.df$exposure <- NULL
names(EBA.df) <- tolower(names(EBA.df))

EBA.df <- mutate(EBA.df,
                  exposure_adj = ifelse(is.na(exposure_default),exposure,exposure-exposure_default))

EBA.df <- mutate(EBA.df,
                  risk_exposure_adj = ifelse(is.na(risk_exposure_default),
                                             risk_exposure,risk_exposure-risk_exposure_default))

## Create Risk weight variable
EBA.df <- mutate(EBA.df,risk_weight = risk_exposure_adj/exposure_adj)


## Remove negative risk weights
EBA.df  <- EBA.df [complete.cases(EBA.df$risk_weight),]
EBA.df  <- EBA.df [EBA.df$risk_weight>0,]

## Create risk calculation method factor
EBA.df <- mutate(EBA.df,approach = factor(ifelse(portfolio==1,"SA","IRB")))
```


## Introduction

**Hypothesis**: capital adequacy arbitrage creates competitive inequalities in the corporate lending market \newline

Our goal:

- Test if credit supply is sensitive to CAR risk-weights \newline

- Disantangle intended from unintended differences in risk-weights and their effect on lending

## Capital Adequacy Ratio and Risk-weights

$CAR=\frac{K}{\sum_i\alpha_i  x_i}\geq k$ \newline

$K$: equity capital \newline
$x_i$: asset $i$ \newline
$\alpha_i$: weight for asset $i$ \newline
$k$: capital ratio requirement \newline


## Risk-weights and Basel Accords

Basel I (July 1988): \newline

- Objectives: strengthen stability and remove competitive inequalities \newline

- Sets fixed risk-weights within asset class \newline

- Leverage ratio:
$\frac{K}{\sum_ix_i}\geq k$ \newline

Problem: portfolio reshuffling increases dispersion in probability of failure [@koehn1980regulation] 

## Risk-weights and Basel Accords

Basel II (2004):

- Introduces the possibility to use internal-based rating (IRB) models to calculate risk-weights 

$CAR=\frac{K}{\sum_i\alpha_i  x_i}\geq k$, \newline

Reason: riskier banks will hold more capital [@kim1988risk] \newline

Problems: 

- Procyclical [@behn2016procyclical]
- Manipulation [@mariathasan2014manipulation; @ferri2017bank;@behn2016limits]


## Risk-weights manipulation: IRB vs SA

```{r density_rw, echo=FALSE}

p <- ggplot(data = subset(EBA.df,subset = risk_weight < 2),
            mapping = aes(x = risk_weight, fill = approach, color = approach)) 
p + geom_density(alpha = 0.3) + 
  labs(x = "Risk-weight",
         title = "Risk-weight density by method") +
  theme_bw()
```

## Risk-weights and Basel Accords

\transparent{0.4}Basel I (July 1988): \newline
- Objectives: strengthen stability and \transparent{1}**remove competitive inequalities** \newline
\transparent{0.4}- Sets fixed risk-weights within asset class \newline

- Leverage ratio:
$\frac{K}{\sum_ix_i}\geq k$, \newline

Problem: portfolio reshuffling increases dispersion in probability of failure [@kim1988risk] 


## Risk-weight manipulation across jurisdiction

```{r box_plot_host, echo=FALSE}

p <- ggplot(data = bank.df,
            mapping = aes(x = reorder(nsa, risk_weight,FUN = median, na.rm=TRUE),
                          y = risk_weight,fill=approach))
p + geom_boxplot() +
    labs(x=NULL) +
    coord_flip() +
  labs(
       y =  "Risk-weight",
         title = "Risk-weight distribution by lender's country and method") +
  theme_bw()
```

## Risk-weight across borrower's country

```{r box_plot_dest, echo=FALSE}

p <- ggplot(data = subset(bank.df,subset = approach == "IRB"),
            mapping = aes(x = reorder(iso_code, risk_weight,FUN = median, na.rm=TRUE),
                          y = risk_weight,fill=approach))
p + geom_boxplot() +
    labs(x=NULL) +
    coord_flip() +
    labs(
       y =  "Risk-weight",
         title = "Risk-weight distribution by borrower's country") +
  theme_bw()
```

## Risk-weight across borrower's and lender's country 

```{r density_rw_countries, echo=FALSE}
EBA_graph.df <- EBA.df %>%
  subset(subset = nsa == "ES" | nsa == "DE") %>%
  subset(subset = approach == "IRB") %>%
  subset(iso_code == "DE" |iso_code == "ES" | iso_code == "FR"| iso_code == "GB")

p <- ggplot(data = EBA_graph.df,
            mapping = aes(x = risk_weight, fill = nsa, color = nsa)) 
p + geom_density(alpha = 0.3) + 
  labs(x = "Risk-weight",
         title = "Risk-weight density for Spanish and German banks in four countries") +
  facet_wrap(~ iso_code, ncol = 4)+
  scale_x_continuous(limits = c(0, 1.1))+
  theme_bw()
```


## Risk-weights and credit risk

```{r rw_default, echo=FALSE}
plot1 <- ggplot(data = subset(bank.df,subset = approach == "IRB"),
            mapping = aes(x = default_rate,
                          y=risk_weight))
plot1 + geom_point() + geom_smooth(method = "lm") +
  labs(x = "Default rate", y = "Risk-weight") +
  theme_bw()

```


## Risk-weight and regulatory standard

```{r rw_avgrw, echo=FALSE}
plot1.df <- bank.df %>%
  subset(subset = approach == "IRB") %>%
  subset(mean.rw.host_dest> 0  )

plot1 <- ggplot(plot1.df,mapping = aes(x = mean.rw.host_dest,
                              y=risk_weight)) 
plot1 + geom_point() + geom_smooth(method = "lm") +
  labs(x = "Average risk-weight across host-destinations exposures", y = "Risk-weight") +
  theme_bw()

```



## Empirical strategy

**Hypothesis**: capital adequacy arbitrage creates competitive inequalities in the corporate lending market \newline

First stage: \newline

$RW_{i,c(l)}=\gamma_1Default_{i,c(l)}+\gamma_2\overline{RW}_{i,c(l)}+\alpha_{i}+\varepsilon_{i,c(l)}$ \newline

Second stage: \newline

$log(Loan_{i,l})=\beta\widehat{RW}_{i,c(l)}+\alpha_{l}+\alpha_{i}+\varepsilon_{i,l}$ \newline

## Summary statistics

```{r summary_loan,eval=TRUE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
bank.df %>% 
  subset(subset = approach == "IRB",
         select = c("loan.amount","risk_weight","default_rate","ssm.dummy")) %>%
  as.data.frame() %>%
stargazer(header = FALSE, type="latex", single.row = TRUE, column.sep.width = "1pt", font.size = "footnotesize",
          omit.summary.stat = c("p25","p75"),
          covariate.labels = c("Loan amount (mn EUR)","Risk-weight","Default rate", "SSM"))
``` 

## Results 



```{r hdfe,echo=FALSE}
rw <- bank.df %>% 
  subset(subset = approach == "IRB",
         select = c("risk_weight")) 

reg.hdfe1 <- felm(log(loan.amount)~ risk_weight | id +period|0|0,
                 data = subset(bank.df ,subset = approach == "IRB" & loan.amount>0))
robust.hdfe1 <- summary(reg.hdfe1,robust=TRUE)$coefficients[,2]
sd.effect1 <- round(100*sd(rw$risk_weight)*(exp(1)^summary(reg.hdfe1,robust=TRUE)$coefficients[1,1]-1),1)

reg.hdfe2 <- felm(log(loan.amount)~risk_weight  | tranche.id +id|0|0,
                 data = subset(bank.df ,subset = approach == "IRB" & loan.amount>0))
robust.hdfe2 <- summary(reg.hdfe2,robust=TRUE)$coefficients[,2]
sd.effect2 <- round(100*sd(rw$risk_weight)*(exp(1)^summary(reg.hdfe2,robust=TRUE)$coefficients[1,1]-1),1)

reg.hdfe3 <- felm(log(loan.amount)~ risk_weight +log(exposure) | tranche.id +id |0|0,
                 data = subset(bank.df ,subset = approach == "IRB" & loan.amount>0))
robust.hdfe3 <- summary(reg.hdfe3,robust=TRUE)$coefficients[,2]
sd.effect3 <- round(100*sd(rw$risk_weight)*(exp(1)^summary(reg.hdfe3,robust=TRUE)$coefficients[1,1]-1),1)

reg.hdfe4 <- felm(log(loan.amount)~ risk_weight  | tranche.id +id |0|0,
                 data = subset(bank.df ,subset = approach == "SA" & loan.amount>0))
robust.hdfe4 <- summary(reg.hdfe4,robust=TRUE)$coefficients[,2]
sd.effect4 <- round(100*sd(rw$risk_weight)*(exp(1)^summary(reg.hdfe4,robust=TRUE)$coefficients[1,1]-1),1)

sd.effect <- c("SD effect", paste0(as.character(sd.effect1),"\\%"),
               paste0(as.character(sd.effect2),"\\%"), 
               paste0(as.character(sd.effect3),"\\%"),
               paste0(as.character(sd.effect4),"\\%"))


```

```{r reg_table,eval=TRUE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}


stargazer(reg.hdfe1,reg.hdfe2,reg.hdfe3,reg.hdfe4,
          header = FALSE, type="latex", align = TRUE, keep.stat = c("n","rsq"), font.size = "tiny", 
          label = "",se = list(robust.hdfe1,robust.hdfe2,robust.hdfe3), style = "qje",
          covariate.labels = c("Risk-weight","log(exposure)"),
          dep.var.labels = "log(Loan amount)", column.sep.width = "2pt",
          column.labels   = c("IRB", "IRB","IRB", "SA"),
          add.lines = list(c("Bank FE", "Yes", "Yes","Yes","Yes"),
                           c("Time FE", "Yes", "-","-","-"),
                           c("Loan FE", "No", "Yes","Yes","Yes"),
                           sd.effect))

```

## Results 

```{r hdfe_iv2,echo=FALSE}


reg.hdfe1 <- felm(log(loan.amount)~ 1 | tranche.id +id |(risk_weight~ default_rate + mean.rw.host_dest)|0,
                 data = subset(bank.df ,subset = approach == "IRB" & loan.amount>0))
robust.hdfe1.s1 <- summary(reg.hdfe1$stage1,robust=TRUE)$coefficients[,2]
robust.hdfe1 <- summary(reg.hdfe1,robust=TRUE)$coefficients[,2]
sd.effect1 <- round(100*sd(rw$risk_weight)*(exp(1)^summary(reg.hdfe1,robust=TRUE)$coefficients[1,1]-1),1)

F.test1 <- round(t(sapply(reg.hdfe1$stage1$lhs, function(lh) waldtest(reg.hdfe1$stage1, ~ default_rate | mean.rw.host_dest, lhs=lh)))[,5],1)

reg.hdfe2 <- felm(log(loan.amount)~ log(exposure) | tranche.id +id |(risk_weight~ default_rate + mean.rw.host_dest)|0, 
                  data = subset(bank.df ,subset = approach == "IRB" & loan.amount>0))
robust.hdfe2.s1 <- summary(reg.hdfe2$stage1,robust=TRUE)$coefficients[,2]
robust.hdfe2 <- summary(reg.hdfe2,robust=TRUE)$coefficients[,2]
sd.effect2 <- round(100*sd(rw$risk_weight)*(exp(1)^summary(reg.hdfe2,robust=TRUE)$coefficients[2,1]-1),1)

F.test2 <- round(t(sapply(reg.hdfe2$stage1$lhs, function(lh) waldtest(reg.hdfe2$stage1, ~ default_rate | mean.rw.host_dest, lhs=lh)))[,5],1)

sd.effect <- c("SD effect", "",
               paste0(as.character(sd.effect1),"\\%"),
               "",
               paste0(as.character(sd.effect2),"\\%"))
F.test <- c("F-test",as.character(F.test1),"",
            as.character(F.test2),"")

```

```{r reg_table_iv2,eval=TRUE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}


stargazer(reg.hdfe1$stage1,reg.hdfe1,reg.hdfe2$stage1,reg.hdfe2,
          header = FALSE, type="latex", align = TRUE, keep.stat = c("n","f","rsq"), font.size = "tiny", 
          label = "",se = list(robust.hdfe1.s1,robust.hdfe1,robust.hdfe2.s1,robust.hdfe2),
          covariate.labels = c("Risk-weight","Default rate","Mean risk-weight","log(exposure)"),
          order = c("risk_weight","default_rate","mean.rw.host_dest","log(exposure)"),
          dep.var.labels = c("Risk-weight","log(Loan amount)","Risk-weight","log(Loan amount)"), style = "qje",
          column.labels   = c("First stage", "Second stage","First stage", "Second stage"),
          column.sep.width = "3pt",
          add.lines = list(c("Bank FE", "Yes", "Yes","Yes","Yes"),
                           c("Time FE", "Yes", "-","Yes","-"),
                           c("Loan FE", "No", "Yes","No","Yes"),
                           sd.effect,F.test))

```

## Results

```{r hdfe_iv,echo=FALSE}


iv.help <- bank.df %>%
  subset(subset = approach == "IRB") %>%
  distinct(eba,iso_code,period,.keep_all = TRUE)

reg.hdfe1 <- felm(risk_weight~ default_rate + mean.rw.host_dest +log(exposure)  | period +id|0|0,
                 data = iv.help)
robust.hdfe1 <- summary(reg.hdfe1,robust=TRUE)$coefficients[,2]
F.test1 <- round(t(sapply(reg.hdfe1$lhs, function(lh) waldtest(reg.hdfe1, ~ default_rate | mean.rw.host_dest, lhs=lh)))[,5],1)

iv.help$rw.fv <- reg.hdfe1$fitted.values
iv.help <- subset(iv.help,select = c("rw.fv","eba","iso_code","period"))
bank.df <- merge(bank.df,iv.help,by=c("eba","iso_code","period"),all = TRUE)

reg.hdfe2 <- felm(log(loan.amount)~ rw.fv +log(exposure) | tranche.id +id |0|0,
                 data = subset(bank.df ,subset = approach == "IRB" & loan.amount>0))
robust.hdfe2 <- summary(reg.hdfe2,robust=TRUE)$coefficients[,2]
sd.effect2 <- round(100*sd(reg.hdfe1$fitted.values)*(exp(1)^summary(reg.hdfe2,robust=TRUE)$coefficients[1,1]-1),1)



sd.effect <- c("SD effect", "",
               paste0(as.character(sd.effect2),"\\%"))

F.test <- c("F-test",as.character(F.test1),"")
```

```{r reg_table_iv,eval=TRUE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}


stargazer(reg.hdfe1,reg.hdfe2,
          header = FALSE, type="latex", align = TRUE, keep.stat = c("n","f","rsq"), font.size = "tiny", 
          label = "",se = list(robust.hdfe1,robust.hdfe2),
          covariate.labels = c("Default rate","Mean risk-weight","Risk-weight","log(exposure)"),
          dep.var.labels = c("Risk-weight","log(Loan amount)"), style = "qje",
          column.labels   = c("First stage", "Second stage"),
          column.separate = c(1, 1), column.sep.width = "5pt",
          add.lines = list(c("Bank FE", "Yes", "Yes","Yes"),
                           c("Time FE", "Yes", "-","-"),
                           c("Loan FE", "No", "Yes","Yes"),
                           sd.effect,F.test))

```
## Results

```{r hdfe_iv3,echo=FALSE}


iv.help <- bank.df %>%
  subset(subset = approach == "IRB") %>%
  distinct(eba,iso_code,period,.keep_all = TRUE)

reg.hdfe1 <- felm(risk_weight~ default_rate  | 0|0|0,
                 data = iv.help)
robust.hdfe1 <- summary(reg.hdfe1,robust=TRUE)$coefficients[,2]
F.test1 <- round(t(sapply(reg.hdfe1$lhs, function(lh) waldtest(reg.hdfe1, ~ default_rate, lhs=lh)))[,5],1)

reg.hdfe2 <- felm(risk_weight~  mean.rw.host_dest   | 0|0|0,
                 data = iv.help)
robust.hdfe2 <- summary(reg.hdfe2,robust=TRUE)$coefficients[,2]
F.test2 <- round(t(sapply(reg.hdfe2$lhs, function(lh) waldtest(reg.hdfe2, ~  mean.rw.host_dest, lhs=lh)))[,5],1)

iv.help$rw.fv.default <- reg.hdfe1$fitted.values
iv.help$rw.fv.manipulation <- reg.hdfe2$fitted.values

iv.help <- subset(iv.help,select = c("rw.fv.default","rw.fv.manipulation","eba","iso_code","period"))
bank.df <- merge(bank.df,iv.help,by=c("eba","iso_code","period"),all = TRUE)

reg.hdfe3 <- felm(log(loan.amount)~ rw.fv.default+rw.fv.manipulation  | tranche.id +id |0|0,
                 data = subset(bank.df ,subset = approach == "IRB" & loan.amount>0))
robust.hdfe3 <- summary(reg.hdfe3,robust=TRUE)$coefficients[,2]
sd.effect1 <- round(100*sd(reg.hdfe1$fitted.values)*(exp(1)^summary(reg.hdfe3,robust=TRUE)$coefficients[1,1]-1),1)
sd.effect2 <- round(100*sd(reg.hdfe2$fitted.values)*(exp(1)^summary(reg.hdfe3,robust=TRUE)$coefficients[2,1]-1),1)



sd.effect.risk <- c("SD effect (risk)", "","",
               paste0(as.character(sd.effect1),"\\%"))
sd.effect.avg <- c("SD effect (avg.)", "","",
               paste0(as.character(sd.effect2),"\\%"))

F.test <- c("F-test",as.character(F.test1),as.character(F.test1),"")
```

```{r reg_table_iv3,eval=TRUE, echo=FALSE, results='asis', warning=FALSE, message=FALSE}


stargazer(reg.hdfe1,reg.hdfe2,reg.hdfe3,
          header = FALSE, type="latex", align = TRUE, keep.stat = c("n","f","rsq"), font.size = "tiny", 
          label = "",se = list(robust.hdfe1,robust.hdfe2,robust.hdfe3),
          covariate.labels = c("Default rate","Mean risk-weight","Risk-weight (risk)","Risk-weight (avg.)"),
          dep.var.labels = c("Risk-weight","log(Loan amount)"), style = "qje",
          column.labels   = c("First stage", "Second stage"),
          column.separate = c(2, 1), column.sep.width = "5pt",
          add.lines = list(c("Bank FE", "No", "No","Yes"),
                           c("Loan FE", "No", "No","Yes"),
                           sd.effect.risk,sd.effect.avg,F.test))

```


## References
\tiny
